Openness and computational reproducibility in plant pathology: where we stand and a way forward

### 2023-01-03 analysis/paper/paper.Rmd
Reword statistical analysis findings for clarity again after in put from Tin
Add Tin to acknowledgements

The null hypothesis that the year of publication had no effect on the availability of data was not rejected.
The analysis found that there was no effect of year of publication on the availability of data (Median = 0.08, 95% CI [-8.06e-03, 0.18]) with a 96.19% probability of being positive (\> 0), 75.92% of being significant (\> 0.05), and 0.00% of being large (\> 0.30) (Figure \@ref(fig:year-parameters)B, Table S4).
The estimation successfully converged (Rhat = 1.000) and the indices were reliable (ESS = 21692).

@@

The authors are grateful for insightful comments from Dr David Ferris and Dr Rebecca O'Leary the USQ Centre for Crop Health Advisory Group on the final manuscript that helped improve the paper and from Ms Anna Hepworth for statistical guidance on evaluating inter-rater scores and for the comments from the anonymous reviewers and Dr Nian Wang that greatly improved the quality of this manuscript.

>>>>

We failed to reject the null hypothesis that the year of publication had no effect on the availability of data.
The analysis found that there was no effect of year of publication on the availability of data (Median = 0.08, 95% CI [-8.06e-03, 0.18]) with a 96.19% probability of being positive (\> 0), 75.92% of being significant (\> 0.05), and 0.00% of being large (\> 0.30) (Figure \@ref(fig:year-parameters)B, Table S4).
The estimation successfully converged (Rhat = 1.000) and the indices were reliable (ESS = 21692).

@@

The authors are grateful for insightful comments from Dr David Ferris, Dr Rebecca O'Leary, Mr Tinula Kariyawasam and the USQ Centre for Crop Health Advisory Group on the final manuscript that helped improve the paper and from Ms Anna Hepworth for statistical guidance on evaluating inter-rater scores and for the comments from the anonymous reviewers and Dr Nian Wang that greatly improved the quality of this manuscript.
